---
title: "How does the new policy at Polymensa restricting second servings impact the amount of food waste generated by students, when compared to the previous policy allowing second servings?"
date: today
author:
  - name: Nicolas Bartzsch
    orcid: 0009-0003-8702-2500
    email: nbartzsch@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
license: "CC BY"
citation: 
  container-title: My Blog
  url: https://www.example.com
bibliography: references.bib
csl: apa.csl
editor: visual
format:
  html:
    toc: true
execute: 
  warning: false
---

# Introduction

According to @scherhaufer2018environmental close to 88 Million tonnes of food waste is produced every year in the European Union alone. This is should be a major concern to all, since wasting food also means losing valuable resources and causing environmental impacts as described by @tonini2018environmental. This also sparks discussions at Swiss universities. Recent modifications to ETH Zürichs Polymensa food policy, have imposed restrictions on second servings. The new policy is criticized by some students, with many voicing their concerns and arguing that the new policy may not effectively reduce food waste as intended by the Mensa. In this study we investigate the impact of this new policy on the perceived amount of food waste generated by students.

# Methods

All of the data gathered for this project was obtained through a voluntary online survey, targeted at students who frequent the Polymensa. The survey, and therefore the data collection, was completely anonymous and consisted of 10 questions. In total, 12 subjects participated in this study, which has to be kept in mind when interpreting the obtained data. The further data processing was completely done in R, considering the recommendations for tidy data from @wickham2014tidya.

# Results

```{r}
#| echo: false

#load packages
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(ggridges)
```

In the follwing the results will be summarized using some figures and tables

```{r}
#| label: fig-likliness
#| fig-cap: "This figure shows the correlation between the likleyness of food waste and the willingness of a participant to choose a smaller serving"

#Import data for plot
final_data <- read_csv(here::here("data/final/final_data.csv"))

#Plotting data
ggplot(data = mensa_food_waste_clean,
       mapping = aes(x = second_serving,
                     fill = compare_fw)) +
  geom_bar()+
  scale_color_colorblind()+
  theme_minimal()

```

# Conclusions

Conlucions are in this section

# References
